Mixture Models for Single-Cell Assays with Application to Vaccine Studies: Supplementary Materials

### 2013-05-15 SupplementaryMaterialMIMOSA.tex
Updated figure S1

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
%   \includegraphics[width=.75\columnwidth]{Figures/2}\\
%   \includegraphics[width=.75\columnwidth]{Figures/12}
\begin{tikzpicture} [auto, node distance=0cm]
 \node at (0,) (A) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=.5\columnwidth]{Figures/3.pdf}};
        \begin{scope}[x={(b.south east)},y={(b.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {A} ;
                \end{scope}
        \end{tikzpicture}
 };
 \node [right=of A] (B) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (c) {\includegraphics[width=.5\columnwidth]{Figures/5.pdf}};
        \begin{scope}[x={(c.south east)},y={(c.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {B} ;
        \end{scope}
        \end{tikzpicture}
};
\node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=.5\columnwidth]{Figures/6.pdf}};
        \begin{scope}[x={(d.south east)},y={(d.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {C} ;
                \end{scope}
        \end{tikzpicture}
};
\node [right=of C] (D) {
\begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (e) {\includegraphics[width=.5\columnwidth]{Figures/7.pdf}};
        \begin{scope}[x={(d.south east)},y={(d.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {D} ;
                \end{scope}
        \end{tikzpicture}
 };
   % \node[anchor=south west, inner sep=0] at (8,-7.5){\includegraphics[width=.5\columnwidth]{Figures/8}};
   % \node[anchor=south west, inner sep=0] at (0,-11.25){\includegraphics[width=.5\columnwidth]{Figures/9}};
    %\node[anchor=south west, inner sep=0] at (8,-11.25){\includegraphics[width=.5\columnwidth]{Figures/10}};
    %\node[anchor=south west, inner sep=0] at (0,-15){\includegraphics[width=.5\columnwidth]{Figures/11}};
    %\node[anchor=south west, inner sep=0] at (8,-15){\includegraphics[width=.5\columnwidth]{Figures/13}};

>>>>

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
%   \includegraphics[width=.75\columnwidth]{Figures/2}\\
%   \includegraphics[width=.75\columnwidth]{Figures/12}
\begin{tikzpicture} [auto, node distance=0cm]
 \node at (0,) (A) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=.5\columnwidth]{Figures/revised_3.pdf}};
        \begin{scope}[x={(b.south east)},y={(b.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {A} ;
                \end{scope}
        \end{tikzpicture}
 };
 \node [right=of A] (B) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (c) {\includegraphics[width=.5\columnwidth]{Figures/revised_5.pdf}};
        \begin{scope}[x={(c.south east)},y={(c.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {B} ;
        \end{scope}
        \end{tikzpicture}
};
\node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=.5\columnwidth]{Figures/revised_6.pdf}};
        \begin{scope}[x={(d.south east)},y={(d.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {C} ;
                \end{scope}
        \end{tikzpicture}
};
\node [right=of C] (D) {
\begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (e) {\includegraphics[width=.5\columnwidth]{Figures/revised_7.pdf}};
        \begin{scope}[x={(d.south east)},y={(d.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {D} ;
                \end{scope}
        \end{tikzpicture}
 };
   % \node[anchor=south west, inner sep=0] at (8,-7.5){\includegraphics[width=.5\columnwidth]{Figures/8}};
   % \node[anchor=south west, inner sep=0] at (0,-11.25){\includegraphics[width=.5\columnwidth]{Figures/9}};
    %\node[anchor=south west, inner sep=0] at (8,-11.25){\includegraphics[width=.5\columnwidth]{Figures/10}};
    %\node[anchor=south west, inner sep=0] at (0,-15){\includegraphics[width=.5\columnwidth]{Figures/11}};
    %\node[anchor=south west, inner sep=0] at (8,-15){\includegraphics[width=.5\columnwidth]{Figures/13}};
